\section{Presentations}

\textbf{Conference Talks}
\orderedouterlist{

\entry{\textbf{Shang, S.}, \& Petrocelli, J. V. (2020, October). \textit{Detecting Bullshit: The Roles of Response Latency and Topic Complexity}. Data Byte presented at the 43rd annual convention of the Society of Southeastern Social Psychologists, Virtual.}

\entry{\textbf{Shang, S.}, Huang, P., Kathmandu, A., McCandliss, B., \& Cohen, G. L. (2018, October). \textit{Stereotype Threat Benefited Women in Unpredictable Tasks, and Hurt them in Predictable Ones}. Individual talk presented at the 41st annual convention of the Society of Southeastern Social Psychologists, Raleigh, NC.}

}


% \textbf{Invited Talks}


\textbf{Conference Presentations}
\orderedouterlist{
\entry{Brocato, N., Rue, P., \textbf{Shang, S.}, \& Zhao, Y. (2021, March). \textit{Using National Data on Students’ Wellbeing and Experiences with Discrimination to Improve Your Campus Community Climate}. Presented at the NASPA Annual Conference, Virtual.}

\entry{Wang, D., \textbf{Shang, S.}, Zhou, R., Lu, Y., Meng, T., \& Li, X. (2021, February). \textit{Evaluating a Meditation-based Employee Assistance Program (EAP) in a High-stake, High-risk Working Environment}. Poster presented at the Intervention Science preconference of the 22nd annual convention of the Society for Personality and Social Psychology, Virtual.}

\entry{\textbf{Shang, S.}, \& Petrocelli, J. V. (2020, February). \textit{Bullshitting, Fast and Slow: How Lay Beliefs of Speed Affect Self-Perceptions of Bullshit Behavior}. Poster presented at the 21st annual convention of the Society for Personality and Social Psychology, New Orleans, LA.}

\entry{Petrocelli, J. V., Rice, E. N., \& \textbf{Shang, S.} (2020, February). \textit{Testing the Insidious Bullshit Hypothesis with The Illusory Truth Effect}. Poster presented at the 21st annual convention of the Society for Personality and Social Psychology, New Orleans, LA.}

\entry{\textbf{Shang, S.}, \& Kathmandu, A. (2019, February). \textit{Growth Mindset in China: Antecedents and Effects on Academic Achievement}. Poster presented at the 20th annual convention of the Society for Personality and Social Psychology, Portland, OR.}

\entry{Li, S., Huang, P., Yang, F., \textbf{Shang, S.}, \& Kathmandu, A. (2019, February). \textit{Artificial Intelligence Uncovers the Nature of Knowledge in Psychological Science}. Poster presented at the 20th annual convention of the Society for Personality and Social Psychology, Portland, OR.}

\entry{\textbf{Shang, S.}, Huang, P., Kathmandu, A., McCandliss, B., \& Cohen, G. L. (2018, August). \textit{Stereotype Threat Lowers Performance through Debilitating Preparatory Control Functions}. Poster presented at the annual convention of the American Psychological Association, San Francisco, CA.}

\entry{\textbf{Shang, S.} (2018, May). \textit{Effects of the Confusion between Visual Imagery and Perception on False Memory}. Poster presented at the 30th annual convention of the Association for Psychological Science, San Francisco, CA.}

\entry{\textbf{Shang, S.}, Kathmandu, A., McCandliss, B., \& Cohen, G. L. (2018, March). \textit{The Effect of Negative Gender Stereotype on Easy and Hard Switching Tasks}. Poster presented at the 19th annual convention of the Society for Personality and Social Psychology, Atlanta, GA.}

}

% \entry{ \textit{}. }

\textbf{Departmental Talks \& Presentations}
\orderedouterlist{

\entry{\textbf{Shang, S.}, \& Petrocelli, J. V. (2019, May). \textit{Bullshitting, Fast and Slow: How Lay Beliefs of Speed Affect Self-Perceptions of Bullshit Behavior}. Poster presented at the 2019 WFU First Year Colloquium, Winston-Salem, NC.}

}

